\bfseries Don't interpolate your data!

### 2022-10-23 main.tex
add a figure; notes to self

Because we are often dealing with a spectrograph with a (fairly) well defined spectral resolution ($\delta\lambda/\lambda$ roughly constant), and because we care a lot about Doppler shifts (which are uniform in log wavelength), it makes sense to think of the pixel positions $x_i$ and shifts $\Delta x_i$ as being in log-wavelength (or ln-wavelength) units.
Indeed, the \textsl{Sloan Digital Sky Survey} family of spectrographs extract one-dimensional spectra on a uniform-in-log-wavelength basis.
Once that choice is made, there are still many choices for the linear basis,
which include canonical functions from interpolation bases, wavelets, and Fourier series.
In what follows, somewhat arbitrarily, we will use a Fourier basis, which can be expressed as follows:
\begin{align}
    g_j(x) & = \left\{\begin{array}{cl}\displaystyle\cos\left(\frac{\pi\,[j-1]}{L}\,x\right) & \mbox{for $j$ odd} \\[3ex]
                                       \displaystyle\sin\left(\frac{\pi\,j}{L}\,x\right) & \mbox{for $j$ even}\end{array}\right. ~,
\end{align}
where $L$ is a (long) length-scale in the $x$ space (the log-wavelength space).

@@

\paragraph{Fake data}
We demonstrate the effectiveness of the spectral combination method on artificial data.
The spectral data were generated from a mean spectral expectation that is a continuum plus a randomly generated (not at all physical) line list, where each line equivalent width was set by a random draw from a power law.
Each spectral epoch was given a velocity (Doppler shift) by putting the epochs equally spaced on a sinusoidal variation with a semi-amplitude of $30\,\kmps$ (to emulate the motion of the spectrograph with respect to the Solar System barycenter).
The data were generated with an assumption of unresolved spectral lines and a Gaussian line-spread function (LSF) by simply evaluating the spectral expectation model at pixel centers, so the LSF is effectively the pixel-convolved LSF.
The individual pixel grids $x_i$ were set to slightly under-sample the pixel-convolved LSF, and they were fixed in the rest frame of the spectrograph.
After sampling the mean spectral expectation model at the pixels, we add Gaussian noise with a uniform variance such that the signal-to-noise in the continuum is XXXX per pixel in each epoch spectrum.
At a rate of XXX pixels were randomly and independently marked as ``bad'' and offset by a large offset.

HOGG: MAKE 2 DATA SETS, one poorly sampled, one well sampled.

@@

We show the final result of Standard Practice (tm)---interpolating the input data and then averaging the interpolations---for the two data sets, in \figurename~\ref{fig:standard}.
We also show the comparison with the true spectral expectation model that was employed to make the fake data.
We find HOGG WHAT??
\begin{figure}[t!]
    \begin{mdframed}\begin{center}
    \includegraphics[width=\figurewidth]{notebooks/standard1.pdf}\\
    \includegraphics[width=\figurewidth]{notebooks/standard2.pdf}
    \end{center}
    \caption{Same as \figurename~\ref{fig:forward} but for the output of Standard Practice (tm). Note that the residuals appear to be spatially correlated; more about this in the text and in \figurename~\ref{fig:noise}.\label{fig:standard}}
    \end{mdframed}
\end{figure}

@@

>>>>

Because we are often dealing with a spectrograph with a (fairly) well defined spectral resolution ($\delta\lambda/\lambda$ roughly constant), and because we care a lot about Doppler shifts (which are uniform in log wavelength), it makes sense to think of the pixel positions $x_i$ and shifts $\Delta x_i$ as being in log-wavelength (or ln-wavelength) units.
Indeed, the \textsl{Sloan Digital Sky Survey} family of spectrographs extract one-dimensional spectra on a uniform-in-log-wavelength basis.
Once that choice is made, there are still many choices for the linear basis,
which include canonical functions from interpolation bases, wavelets, and Fourier series.
In what follows, somewhat arbitrarily, we will use a Fourier basis, which can be expressed as follows:
\begin{align}
    g_j(x) & = \left\{\begin{array}{cl}\displaystyle\cos\left(\frac{\pi\,[j-1]}{L}\,x\right) & \mbox{for $j$ odd} \\[3ex]
                                       \displaystyle\sin\left(\frac{\pi\,j}{L}\,x\right) & \mbox{for $j$ even}\end{array}\right. ~,
\end{align}
where $L$ is a (long) length-scale in the $x$ space (the log-wavelength space), and $1\leq j\leq P$.

@@

\paragraph{Fake data}
We demonstrate the effectiveness of the spectral combination method on artificial data.
The spectral data were generated from a mean spectral expectation that is a continuum plus a randomly generated (not at all physical) line list, where each line equivalent width was set by a random draw from a power law.
Each spectral epoch was given a velocity (Doppler shift) by putting the epochs equally spaced on a sinusoidal variation with a semi-amplitude of $30\,\kmps$ (to emulate the motion of the spectrograph with respect to the Solar System barycenter).
The data were generated with an assumption of unresolved spectral lines and a Gaussian line-spread function (LSF) by simply evaluating the spectral expectation model at pixel centers, so the LSF is effectively the pixel-convolved LSF.
After sampling the mean spectral expectation model onto an observational pixel grid, we add Gaussian noise with a uniform variance (HOGG NO WE DON'T!) such that the signal-to-noise in the continuum is XXXX per pixel in each epoch spectrum.
At a rate of XXX pixels were randomly and independently marked as ``bad'' and offset by a large offset.

HOGG: MAKE 2 DATA SETS, one poorly sampled, one well sampled.
The individual pixel grids $x_i$ were set to slightly under-sample the pixel-convolved LSF, and they were fixed in the rest frame of the spectrograph.

@@

We show the final result of Standard Practice (tm)---interpolating the input data and then averaging the interpolations---for the two data sets, in \figurename~\ref{fig:standard}.
We also show the comparison with the true spectral expectation model that was employed to make the fake data.
We find HOGG WHAT?? CORRELATIONS; WORSE RESIDUALS NEAR SPECTRAL FEATURES (UH OH).
\begin{figure}[t!]
    \begin{mdframed}\begin{center}
    \includegraphics[width=\figurewidth]{notebooks/standard1.pdf}\\
    \includegraphics[width=\figurewidth]{notebooks/standard2.pdf}
    \end{center}
    \caption{Same as \figurename~\ref{fig:forward} but for the output of Standard Practice (tm). Note that in the poorly sampled case, the residuals appear to be spatially correlated, and the residuals appear to be larger near strong spectral features; more about these issues in the text and in \figurename~\ref{fig:noise}.\label{fig:standard}}
    \end{mdframed}
\end{figure}

@@

We assumed no sky subtraction necessary. What gives?
